Fusion Moves for Correlation Clustering

### 2014-11-11 paper/egpaper_for_review.tex
made caption on anytime plot more compact
proofs

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

@@

@@

\begin{theorem}[Monotone]
Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
Than $y^*$  will never decrease the energy:
$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
%
\begin{proof}
The feasible set of the fusion move includes per definition  $y'$ and $y''$.
If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
and that why not the propose segmentation of a fusion.
\end{proof}
%
\end{theorem}

>>>>

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

\begin{definition}\emph{(Contradicted Graph)}
Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contradiction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}

\begin{definition}\emph{(Back Projection)}
Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
by 
\begin{align}
\rho^G_{uv}(\bar{y})=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.
\end{align}
\end{definition}

@@

% \begin{theorem}[Monotone]
% Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
% Than $y^*$  will never decrease the energy:
% $y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
% %
% \begin{proof}
% The feasible set of the fusion move includes per definition  $y'$ and $y''$.
% If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
% and that why not the propose segmentation of a fusion.
% \end{proof}
% %
% \end{theorem}
